Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-09 ms.tex
updating figures to new fiducial value of eta=0.2

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item We find that for $\Mbh\gsim 10^6 \Msun$ and $\Mbh\lsim 10^8
    \Msun$, $\eddr \propto \Mbh^{\alpha}$ with $\alpha\lsim
    0.5 \, (0.8)$ for core (cusp) galaxies, 
    following average star formation histories measured in
    cosmological simulations \citep{MosterNaab+:2013a}. This is in
    tension observations of nuclear X-ray luminosity which suggest
    that $\eddr$ increases towards smaller $\Mbh$
    \citep{Miller+15}. However, it is important to note that the
    inflow rate on large scales (which we calculate) may differ from
    the actual accretion rate as outflows could occur on small
    scales. The outflow rate would depend on the angular momentum of
    the infalling gas and thus the angular momentum of stars in the
    nucleus. The in turn would vary systematically with $\Mbh$.
  \item We expect within scatter in nuclear x-ray luminosities at
    fixed $\Mbh$ from (1) stochastic variation in star formation
    history from galaxy to galaxy (2) Variations in small scale outflow
    rates due to variations between galactic nuclear angular momenta.
    These variations alone could explain much of the 2-4 orders of
    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.

>>>>

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item We find that for $\Mbh\gsim 10^6 \Msun$ and $\Mbh\lsim 10^8
    \Msun$, $\eddr \propto \Mbh^{\alpha}$ with $\alpha\lsim
    0.5 \, (0.8)$ for core (cusp) galaxies, 
    following average star formation histories measured in
    cosmological simulations \citep{MosterNaab+:2013a}. This is in
    tension observations of nuclear X-ray luminosity which suggest
    that $\eddr$ increases towards smaller $\Mbh$
    \citep{Miller+15}. However, it is important to note that the
    inflow rate on large scales (which we calculate) may differ from
    the actual accretion rate as outflows could occur on small
    scales. The outflow rate would depend on the angular momentum of
    the infalling gas and thus the angular momentum of stars in the
    nucleus. The in turn would vary systematically with $\Mbh$.
  \item We expect within scatter in nuclear x-ray luminosities at
    fixed $\Mbh$ from (1) stochastic variation in star formation
    history from galaxy to galaxy (2) Variations in small scale outflow
    rates due to variations between galactic nuclear angular
    momenta. {\bf AG: some more explanation of why 1 might not show up
    in Pellegrini...}
    These variations alone could explain much of the 2-4 orders of
    magnitude of scatter of nuclear x-ray luminosity at fixed $\Mbh$ 
    in the samples of \citet{Miller+15} and \citet{Pellegrini:2010a}.
